---
title: Harmonize Knowledge Graph
subtitle: Ayush Noori
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
editor_options: 
  chunk_output_type: inline
---

```{r setup, include = FALSE}
# knitr::opts_chunk$set(eval = FALSE)
```

# Dependencies

Load requisite packages and define directories.

```{r load-packages, message=FALSE, warning=FALSE}
# data manipulation
library(data.table)
library(purrr)
library(magrittr)

# relative file paths
library(here)

# partition data
library(caret)

# graph analysis
library(igraph)
```

Note that directories are relative to the R project path.

```{r define-directores}
# set directories
primeKG_dir = here("Data", "PrimeKG")
neuroKG_dir = here("Data", "NeuroKG")
```

# Read Data

```{r read-neurokg}
# read NeuroKG with cell type nodes
neuroKG_nodes = readRDS(here(neuroKG_dir, "2_enrich_KG", "neuroKG_nodes.RDS"))
neuroKG_edges = readRDS(here(neuroKG_dir, "2_enrich_KG", "neuroKG_edges.RDS"))

# print original node counts
message("Initial Nodes in NeuroKG: ", nrow(neuroKG_nodes))
message("Initial Edges in NeuroKG: ", nrow(neuroKG_edges))
```

Check for any duplicated IDs.

```{r check-ids}
# check that index --> ID mapping is unique
dups = neuroKG_nodes[, .(node_index, node_id, node_type)] %>%
  .[, joint_id := paste(node_id, node_type, sep = "_")] %>%
  unique() %>%
  .[duplicated(joint_id)] %>% 
  .[order(joint_id)]

# print results
message("Number of Duplicate IDs: ", nrow(dups))
```

Take largest connected component (LCC, weakly connected) of graph.

```{r take-lcc}
# convert to igraph object
neuroKG_graph = graph_from_data_frame(neuroKG_edges[, .(x_index, y_index)], directed = TRUE)

# extract LCC
neuroKG_components = components(neuroKG_graph, mode = "weak")
neuroKG_lcc_nodes = V(neuroKG_graph)[which(neuroKG_components$membership == which.max(neuroKG_components$csize))]
neuroKG_lcc = induced.subgraph(neuroKG_graph, neuroKG_lcc_nodes)

# convert back to data frame
neuroKG_lcc_nodes = as_data_frame(neuroKG_lcc, what = c("vertices"))
neuroKG_lcc_edges = as_data_frame(neuroKG_lcc, what = c("edges"))

# filter nodes and edges for LCC
neuroKG_nodes = neuroKG_nodes[node_index %in% neuroKG_lcc_nodes$name]
neuroKG_edges = neuroKG_edges[(x_index %in% neuroKG_lcc_nodes$name) & (y_index %in% neuroKG_lcc_nodes$name)]

# print summary
message("Nodes in LCC: ", nrow(neuroKG_lcc_nodes))
message("Edges in LCC: ", nrow(neuroKG_lcc_edges))
message("Nodes in Filtered NeuroKG: ", nrow(neuroKG_nodes))
message("Edges in Filtered NeuroKG: ", nrow(neuroKG_edges))
```

Create ID look-up table to map old IDs to new, continuous IDs after table modification.

```{r lookup}
# sort by node index
neuroKG_nodes = neuroKG_nodes[order(node_index), ]

# sort by edge index
# unnecessary, since reordered later
neuroKG_edges = neuroKG_edges[order(x_index, y_index), ]

# create lookup table to map new IDs
lookup = data.table(old_index = neuroKG_nodes$node_index, new_index = 1:nrow(neuroKG_nodes) - 1)
saveRDS(lookup, here(neuroKG_dir, "3_harmonize_KG", "primeKG_to_neuroKG_node_index.RDS"))

# remap IDs
neuroKG_nodes$node_index = lookup$new_index[match(neuroKG_nodes$node_index, lookup$old_index)]
neuroKG_edges$x_index = lookup$new_index[match(neuroKG_edges$x_index, lookup$old_index)]
neuroKG_edges$y_index = lookup$new_index[match(neuroKG_edges$y_index, lookup$old_index)]

# reorder again (unnecessary)
neuroKG_nodes = neuroKG_nodes[order(node_index), ]
# neuroKG_edges = neuroKG_edges[order(x_index, y_index), ]
# ordering scheme updated below

# print results
message("Maximum Node Index: ", max(neuroKG_nodes$node_index))
message("Maximum Node Index from Edges: ", max(neuroKG_edges$x_index))
```

# Process NeuroKG

Add full relation column and partition data 80-15-5 into training, validation, and test sets.

```{r add-relation}
# reorder edges
# in case of duplicate edges, order by display_relation
neuroKG_edges = neuroKG_edges[order(pmin(x_index, y_index), pmax(x_index, y_index), display_relation), ]

# function to construct label
construct_label = function(x_index, y_index) {
  if (x_index < y_index) {
    return(paste(x_index, y_index, sep = "_"))
  } else {
    return(paste(y_index, x_index, sep = "_"))
  }
}

# add index label to neuroKG_edges
# note, label does not include direction
# that is, forward and reverse edges have the same label
neuroKG_edges = neuroKG_edges %>%
  .[, index_label := map2(x_index, y_index, construct_label)]

# add direction
neuroKG_edges = neuroKG_edges %>%
  .[, direction := "forward"] %>%
  .[x_index > y_index, direction := "reverse"]

# for reverse direction, append "rev_" to edge relation
neuroKG_edges[direction == "reverse", relation := paste("rev", relation, sep = "_")]

# add full relation column to edge matrix
neuroKG_edges = neuroKG_edges %>%
  .[, edge_index := (1:nrow(neuroKG_edges)) - 1] %>% # zero-indexed
  .[, full_relation := paste(x_type, relation, y_type, sep = ";")]

# reorder columns
setcolorder(neuroKG_edges, c("edge_index", "index_label", "direction", "relation", "display_relation", "full_relation"))

# check for mismatched edges
# all edges with even indices should be forward
# all edges with odd indices should be odd
# each forward edge should immediately be followed by its reverse edge
even_edges = neuroKG_edges[, ifelse(edge_index %% 2 == 0, "forward", "reverse")]
even_mismatch = neuroKG_edges[direction != even_edges]
message("Forward/Reverse Mismatch: ", nrow(even_mismatch))

# # get forward edges
# neuroKG_edges_forward = neuroKG_edges[direction == "forward"]
```

Partition data into training, validation, and test sets. Note that this partition was commented out because the split was performed in Python instead.

```{r partition}
# # partition into training, validation, and test sets
# set.seed(42)
# train_idx = neuroKG_edges_forward[createDataPartition(full_relation, p = 0.8, list = FALSE), edge_index]
# val_idx = neuroKG_edges_forward[!(edge_index %in% train_idx)] %>%
#     .[createDataPartition(full_relation, p = 0.75, list = FALSE), edge_index]
# test_idx = neuroKG_edges_forward[!edge_index %in% c(train_idx, val_idx), edge_index]
# 
# # message results
# message("Training Length: ", length(train_idx), " (", round(length(train_idx)/nrow(neuroKG_edges_forward), 4) * 100, "%)")
# message("Validation Length: ", length(val_idx), " (", round(length(val_idx)/nrow(neuroKG_edges_forward), 4) * 100, "%)")
# message("Test Length: ", length(test_idx), " (", round(length(test_idx)/nrow(neuroKG_edges_forward), 4) * 100, "%)")
# message("Total Forward Edges: ", length(train_idx) + length(val_idx) + length(test_idx))
# 
# # create partition variable for forward edges
# neuroKG_edges = neuroKG_edges %>%
#   .[edge_index %in% test_idx, mask := "test"] %>%
#   .[edge_index %in% train_idx, mask := "train"] %>%
#   .[edge_index %in% val_idx, mask := "val"]
# 
# # check that all edges not included are reverse
# # summary(neuroKG_edges[is.na(mask), direction == "reverse"])
# # max(test_idx, train_idx, val_idx)
# # max(neuroKG_edges[, edge_index])
# 
# # add partition variable for reverse edges
# neuroKG_edges = neuroKG_edges %>%
#   .[(edge_index %in% (test_idx + 1)) & direction == "reverse", mask := "test"] %>%
#   .[(edge_index %in% (train_idx + 1)) & direction == "reverse", mask := "train"] %>%
#   .[(edge_index %in% (val_idx + 1)) & direction == "reverse", mask := "val"]
# 
# # edges not assigned
# message("Edges Not Assigned: ", nrow(neuroKG_edges[is.na(mask)]))
# 
# # print summary
# table(neuroKG_edges$mask)
```

# Save Data

```{r save-neurokg}
# save to file
saveRDS(neuroKG_nodes, here(neuroKG_dir, "3_harmonize_KG", "neuroKG_nodes.RDS"))
saveRDS(neuroKG_edges, here(neuroKG_dir, "3_harmonize_KG", "neuroKG_edges.RDS"))

# save as CSV files
fwrite(neuroKG_nodes, here(neuroKG_dir, "3_harmonize_KG", "neuroKG_nodes.csv"))
fwrite(neuroKG_edges, here(neuroKG_dir, "3_harmonize_KG", "neuroKG_edges.csv"))
```